---
title: "Parameter Recovery"
output: 
  html_document:
    toc: true
    toc_float:
      toc_collapsed: FALSE
      toc_depth: 3
---

## Notes
Parameter estimate bias results for circumplex simulation.  

  * p = theta parameter estimate for common score variable p##
  * c = cos(p) cosine of theta estimate for corresponding common score variable
  * s = sin(p) sine of theta estimate for corresponding common score variable
  * b0  = $\beta$~0~, variance attributable to the general factor
  * b1  = $\beta$~1~, variance attributable to circumplex structure
  
Note, circumplex models generated with values $\beta$~0~ = $\beta$~1~ = .5

  * Estimate Average = Average parameter estimate across 1000 iterations
  * Estimate SD = Standard Deviation of parameter estimate
  * Coverage = 90% confidence interval coverage
  * Average Bias = average bias between generated and estimated parameter
  * MSE = ![](https://wikimedia.org/api/rest_v1/media/math/render/svg/e258221518869aa1c6561bb75b99476c4734108e) 
  
Please direct any questions to [AJ Thurston](mailto:aj@thurston.io)  
Or reach out to me on [Twitter](https://twitter.com/AJThurston)



```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE
)
library(knitr)
library(data.table)
library(kableExtra)
load("results.bias.Rdata")
results.bias <- lapply(results.bias, function(x) { x[c("source", "model", "nvar", "n")] <- NULL; x })
results.bias <- lapply(results.bias, function(x) {setnames(x, old = grep("parm", names(x)), new = "Parameter")})
results.bias <- lapply(results.bias, function(x) {setnames(x, old = grep("mse", names(x)), new = "MSE")})
```
## Circulant Models
### Circulant, 6 Common Scores, N = 200
```{r bias.circ_06_0200}
results.bias$bias.circ_06_0200 %>%
  kbl(align = 'c') %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>%
  column_spec(1, bold = T, border_right = T)
```
[Back to top](#)

### Circulant, 6 Common Scores, N = 500
```{r bias.circ_06_0500}
results.bias$bias.circ_06_0500 %>%
  kbl(align = 'c') %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>%
  column_spec(1, bold = T, border_right = T)
```
[Back to top](#)

### Circulant, 6 Common Scores, N = 1000
```{r bias.circ_06_1000}
results.bias$bias.circ_06_1000 %>%
  kbl(align = 'c') %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>%
  column_spec(1, bold = T, border_right = T)
```
[Back to top](#)

### Circulant, 12 Common Scores, N = 200
```{r bias.circ_12_0200}
results.bias$bias.circ_12_0200 %>%
  kbl(align = 'c') %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>%
  column_spec(1, bold = T, border_right = T)
```
[Back to top](#)

### Circulant, 12 Common Scores, N = 500
```{r bias.circ_12_0500}
results.bias$bias.circ_12_0500 %>%
  kbl(align = 'c') %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>%
  column_spec(1, bold = T, border_right = T)
```
[Back to top](#)

### Circulant, 12 Common Scores, N = 1000
```{r bias.circ_12_1000}
results.bias$bias.circ_12_1000 %>%
  kbl(align = 'c') %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>%
  column_spec(1, bold = T, border_right = T)
```
[Back to top](#)

### Circulant, 24 Common Scores, N = 200
```{r bias.circ_24_0200}
results.bias$bias.circ_24_0200 %>%
  kbl(align = 'c') %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>%
  column_spec(1, bold = T, border_right = T)
```
[Back to top](#)

### Circulant, 24 Common Scores, N = 500
```{r bias.circ_24_0500}
results.bias$bias.circ_24_0500 %>%
  kbl(align = 'c') %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>%
  column_spec(1, bold = T, border_right = T)
```
[Back to top](#)

### Circulant, 24 Common Scores, N = 1000
```{r bias.circ_24_1000}
results.bias$bias.circ_24_1000 %>%
  kbl(align = 'c') %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>%
  column_spec(1, bold = T, border_right = T)
```
[Back to top](#)

### Circulant, 36 Common Scores, N = 200
```{r bias.circ_36_0200}
results.bias$bias.circ_36_0200 %>%
  kbl(align = 'c') %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>%
  column_spec(1, bold = T, border_right = T)
```
[Back to top](#)

### Circulant, 36 Common Scores, N = 500
```{r bias.circ_36_0500}
results.bias$bias.circ_36_0500 %>%
  kbl(align = 'c') %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>%
  column_spec(1, bold = T, border_right = T)
```
[Back to top](#)

### Circulant, 36 Common Scores, N = 1000
```{r bias.circ_36_1000}
results.bias$bias.circ_36_1000 %>%
  kbl(align = 'c') %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>%
  column_spec(1, bold = T, border_right = T)
```
[Back to top](#)

 ## Censored Models
### Censored, 6 Common Scores, N = 200
```{r bias.cens_06_0200}
results.bias$bias.cens_06_0200 %>%
  kbl(align = 'c') %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>%
  column_spec(1, bold = T, border_right = T)
```
[Back to top](#)

### Censored, 6 Common Scores, N = 500
```{r bias.cens_06_0500}
results.bias$bias.cens_06_0500 %>%
  kbl(align = 'c') %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>%
  column_spec(1, bold = T, border_right = T)
```
[Back to top](#)

### Censored, 6 Common Scores, N = 1000
```{r bias.cens_06_1000}
results.bias$bias.cens_06_1000 %>%
  kbl(align = 'c') %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>%
  column_spec(1, bold = T, border_right = T)
```
[Back to top](#)

### Censored, 12 Common Scores, N = 200
```{r bias.cens_12_0200}
results.bias$bias.cens_12_0200 %>%
  kbl(align = 'c') %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>%
  column_spec(1, bold = T, border_right = T)
```
[Back to top](#)

### Censored, 12 Common Scores, N = 500
```{r bias.cens_12_0500}
results.bias$bias.cens_12_0500 %>%
  kbl(align = 'c') %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>%
  column_spec(1, bold = T, border_right = T)
```
[Back to top](#)

### Censored, 12 Common Scores, N = 1000
```{r bias.cens_12_1000}
results.bias$bias.cens_12_1000 %>%
  kbl(align = 'c') %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>%
  column_spec(1, bold = T, border_right = T)
```
[Back to top](#)

### Censored, 24 Common Scores, N = 200
```{r bias.cens_24_0200}
results.bias$bias.cens_24_0200 %>%
  kbl(align = 'c') %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>%
  column_spec(1, bold = T, border_right = T)
```
[Back to top](#)

### Censored, 24 Common Scores, N = 500
```{r bias.cens_24_0500}
results.bias$bias.cens_24_0500 %>%
  kbl(align = 'c') %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>%
  column_spec(1, bold = T, border_right = T)
```
[Back to top](#)

### Censored, 24 Common Scores, N = 1000
```{r bias.cens_24_1000}
results.bias$bias.cens_24_1000 %>%
  kbl(align = 'c') %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>%
  column_spec(1, bold = T, border_right = T)
```
[Back to top](#)

### Censored, 36 Common Scores, N = 200
```{r bias.cens_36_0200}
results.bias$bias.cens_36_0200 %>%
  kbl(align = 'c') %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>%
  column_spec(1, bold = T, border_right = T)
```
[Back to top](#)

### Censored, 36 Common Scores, N = 500
```{r bias.cens_36_0500}
results.bias$bias.cens_36_0500 %>%
  kbl(align = 'c') %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>%
  column_spec(1, bold = T, border_right = T)
```
[Back to top](#)

### Censored, 36 Common Scores, N = 1000
```{r bias.cens_36_1000}
results.bias$bias.cens_36_1000 %>%
  kbl(align = 'c') %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>%
  column_spec(1, bold = T, border_right = T)
```
[Back to top](#)

 ## Clustered Models
### Clustered, 6 Common Scores, N = 200
```{r bias.clus_06_0200}
results.bias$bias.clus_06_0200 %>%
  kbl(align = 'c') %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>%
  column_spec(1, bold = T, border_right = T)
```
[Back to top](#)

### Clustered, 6 Common Scores, N = 500
```{r bias.clus_06_0500}
results.bias$bias.clus_06_0500 %>%
  kbl(align = 'c') %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>%
  column_spec(1, bold = T, border_right = T)
```
[Back to top](#)

### Clustered, 6 Common Scores, N = 1000
```{r bias.clus_06_1000}
results.bias$bias.clus_06_1000 %>%
  kbl(align = 'c') %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>%
  column_spec(1, bold = T, border_right = T)
```
[Back to top](#)

### Clustered, 12 Common Scores, N = 200
```{r bias.clus_12_0200}
results.bias$bias.clus_12_0200 %>%
  kbl(align = 'c') %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>%
  column_spec(1, bold = T, border_right = T)
```
[Back to top](#)

### Clustered, 12 Common Scores, N = 500
```{r bias.clus_12_0500}
results.bias$bias.clus_12_0500 %>%
  kbl(align = 'c') %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>%
  column_spec(1, bold = T, border_right = T)
```
[Back to top](#)

### Clustered, 12 Common Scores, N = 1000
```{r bias.clus_12_1000}
results.bias$bias.clus_12_1000 %>%
  kbl(align = 'c') %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>%
  column_spec(1, bold = T, border_right = T)
```
[Back to top](#)

### Clustered, 24 Common Scores, N = 200
```{r bias.clus_24_0200}
results.bias$bias.clus_24_0200 %>%
  kbl(align = 'c') %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>%
  column_spec(1, bold = T, border_right = T)
```
[Back to top](#)

### Clustered, 24 Common Scores, N = 500
```{r bias.clus_24_0500}
results.bias$bias.clus_24_0500 %>%
  kbl(align = 'c') %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>%
  column_spec(1, bold = T, border_right = T)
```
[Back to top](#)

### Clustered, 24 Common Scores, N = 1000
```{r bias.clus_24_1000}
results.bias$bias.clus_24_1000 %>%
  kbl(align = 'c') %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>%
  column_spec(1, bold = T, border_right = T)
```
[Back to top](#)

### Clustered, 36 Common Scores, N = 200
```{r bias.clus_36_0200}
results.bias$bias.clus_36_0200 %>%
  kbl(align = 'c') %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>%
  column_spec(1, bold = T, border_right = T)
```
[Back to top](#)

### Clustered, 36 Common Scores, N = 500
```{r bias.clus_36_0500}
results.bias$bias.clus_36_0500 %>%
  kbl(align = 'c') %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>%
  column_spec(1, bold = T, border_right = T)
```
[Back to top](#)

### Clustered, 36 Common Scores, N = 1000
```{r bias.clus_36_1000}
results.bias$bias.clus_36_1000 %>%
  kbl(align = 'c') %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>%
  column_spec(1, bold = T, border_right = T)
```
[Back to top](#)

 ## Unidimensional Models
### Unid., 6 Common Scores, N = 200
```{r bias.unid_06_0200}
results.bias$bias.unid_06_0200 %>%
  kbl(align = 'c') %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>%
  column_spec(1, bold = T, border_right = T)
```
[Back to top](#)

### Unid., 6 Common Scores, N = 500
```{r bias.unid_06_0500}
results.bias$bias.unid_06_0500 %>%
  kbl(align = 'c') %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>%
  column_spec(1, bold = T, border_right = T)
```
[Back to top](#)

### Unid., 6 Common Scores, N = 1000
```{r bias.unid_06_1000}
results.bias$bias.unid_06_1000 %>%
  kbl(align = 'c') %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>%
  column_spec(1, bold = T, border_right = T)
```
[Back to top](#)

### Unid., 12 Common Scores, N = 200
```{r bias.unid_12_0200}
results.bias$bias.unid_12_0200 %>%
  kbl(align = 'c') %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>%
  column_spec(1, bold = T, border_right = T)
```
[Back to top](#)

### Unid., 12 Common Scores, N = 500
```{r bias.unid_12_0500}
results.bias$bias.unid_12_0500 %>%
  kbl(align = 'c') %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>%
  column_spec(1, bold = T, border_right = T)
```
[Back to top](#)

### Unid., 12 Common Scores, N = 1000
```{r bias.unid_12_1000}
results.bias$bias.unid_12_1000 %>%
  kbl(align = 'c') %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>%
  column_spec(1, bold = T, border_right = T)
```
[Back to top](#)

### Unid., 24 Common Scores, N = 200
```{r bias.unid_24_0200}
results.bias$bias.unid_24_0200 %>%
  kbl(align = 'c') %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>%
  column_spec(1, bold = T, border_right = T)
```
[Back to top](#)

### Unid., 24 Common Scores, N = 500
```{r bias.unid_24_0500}
results.bias$bias.unid_24_0500 %>%
  kbl(align = 'c') %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>%
  column_spec(1, bold = T, border_right = T)
```
[Back to top](#)

### Unid., 24 Common Scores, N = 1000
```{r bias.unid_24_1000}
results.bias$bias.unid_24_1000 %>%
  kbl(align = 'c') %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>%
  column_spec(1, bold = T, border_right = T)
```
[Back to top](#)

### Unid., 36 Common Scores, N = 200
```{r bias.unid_36_0200}
results.bias$bias.unid_36_0200 %>%
  kbl(align = 'c') %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>%
  column_spec(1, bold = T, border_right = T)
```
[Back to top](#)

### Unid., 36 Common Scores, N = 500
```{r bias.unid_36_0500}
results.bias$bias.unid_36_0500 %>%
  kbl(align = 'c') %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>%
  column_spec(1, bold = T, border_right = T)
```
[Back to top](#)

### Unid., 36 Common Scores, N = 1000
```{r bias.unid_36_1000}
results.bias$bias.unid_36_1000 %>%
  kbl(align = 'c') %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>%
  column_spec(1, bold = T, border_right = T)
```
[Back to top](#)

 ## Higher-Order Models
### Higher-Order, 6 Common Scores, N = 200
```{r bias.high_06_0200}
results.bias$bias.high_06_0200 %>%
  kbl(align = 'c') %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>%
  column_spec(1, bold = T, border_right = T)
```
[Back to top](#)

### Higher-Order, 6 Common Scores, N = 500
```{r bias.high_06_0500}
results.bias$bias.high_06_0500 %>%
  kbl(align = 'c') %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>%
  column_spec(1, bold = T, border_right = T)
```
[Back to top](#)

### Higher-Order, 6 Common Scores, N = 1000
```{r bias.high_06_1000}
results.bias$bias.high_06_1000 %>%
  kbl(align = 'c') %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>%
  column_spec(1, bold = T, border_right = T)
```
[Back to top](#)

### Higher-Order, 12 Common Scores, N = 200
```{r bias.high_12_0200}
results.bias$bias.high_12_0200 %>%
  kbl(align = 'c') %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>%
  column_spec(1, bold = T, border_right = T)
```
[Back to top](#)

### Higher-Order, 12 Common Scores, N = 500
```{r bias.high_12_0500}
results.bias$bias.high_12_0500 %>%
  kbl(align = 'c') %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>%
  column_spec(1, bold = T, border_right = T)
```
[Back to top](#)

### Higher-Order, 12 Common Scores, N = 1000
```{r bias.high_12_1000}
results.bias$bias.high_12_1000 %>%
  kbl(align = 'c') %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>%
  column_spec(1, bold = T, border_right = T)
```
[Back to top](#)

### Higher-Order, 24 Common Scores, N = 200
```{r bias.high_24_0200}
results.bias$bias.high_24_0200 %>%
  kbl(align = 'c') %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>%
  column_spec(1, bold = T, border_right = T)
```
[Back to top](#)

### Higher-Order, 24 Common Scores, N = 500
```{r bias.high_24_0500}
results.bias$bias.high_24_0500 %>%
  kbl(align = 'c') %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>%
  column_spec(1, bold = T, border_right = T)
```
[Back to top](#)

### Higher-Order, 24 Common Scores, N = 1000
```{r bias.high_24_1000}
results.bias$bias.high_24_1000 %>%
  kbl(align = 'c') %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>%
  column_spec(1, bold = T, border_right = T)
```
[Back to top](#)

### Higher-Order, 36 Common Scores, N = 200
```{r bias.high_36_0200}
results.bias$bias.high_36_0200 %>%
  kbl(align = 'c') %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>%
  column_spec(1, bold = T, border_right = T)
```
[Back to top](#)

### Higher-Order, 36 Common Scores, N = 500
```{r bias.high_36_0500}
results.bias$bias.high_36_0500 %>%
  kbl(align = 'c') %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>%
  column_spec(1, bold = T, border_right = T)
```
[Back to top](#)

### Higher-Order, 36 Common Scores, N = 1000
```{r bias.high_36_1000}
results.bias$bias.high_36_1000 %>%
  kbl(align = 'c') %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>%
  column_spec(1, bold = T, border_right = T)
```
[Back to top](#)